---
title: "Experimenting with co-kriging"
author: "Lara Wootton"
date: "5/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
setwd("/Users/larawootton/Documents/Honours/Data")

if(!require(pacman)){install.packages("pacman", dependencies=TRUE); library(pacman)}
p_load(dplyr, ggplot2, RColorBrewer, sp, lattice, munsell, gstat, automap, cowplot)

source("/Users/larawootton/Documents/Honours/Project_analysis/to_be_sourced.R")
rm(species_df)

my_soil_df <- my_soil_df %>% mutate(MgSqrt = sqrt(Mg))
my_grid <- my_soil_df %>% filter(type == "grid")

theme_set(theme_bw())
my_theme <- theme(
  #axis.title.x = element_blank(),
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  panel.grid = element_blank()
)
my_colour <- scale_color_distiller(palette = "YlOrRd", direction = 0)

```

###Summary

* Co-kriging with all three colour metrics generally reduced the R squared compared to ordinary kriging.   

* Co-kriging with one colour matric resulted in similar R squared values to ordinary kriging.

* The average R squared value was just over 0.6.
However, there generally wasn't a one to one ratio between predicted and observed values.

* Kriging over data per site rather than all three sites at once had mixed results. It improved the model for site 2, but the model for site 3 was much worse.   



####Co kriging assumptions

The target variable must be

* Normally distributed
* Stationary - local variation doesn’t change in different areas of the map
* No trends

The co variables must have

* a feature-space correlation with the target variable
* a spatial structure (i.e. be modelled as a regional variable)
* a spatial co-variance with the target variable

Not 100% sure how to check most of those assumptions, but let's check normality.
```{r}
par(mfrow=c(1,3))
hist(my_grid$Mg, main = "", xlab = "Mg")
hist(log(my_grid$Mg), main = "", xlab = "log Mg")
hist(sqrt(my_grid$Mg), main = "", xlab = "sqrt Mg")
```

I'm going to be working with the sqrt transformed data, as they seem most normal.

Let's look at the observed values

```{r}
my_soil_df %>% as.data.frame() %>% 
  ggplot(aes(lon, lat, colour = MgSqrt)) +
  geom_point(size = 4) +
  my_colour
```


Package automap automatically fits variograms and krige

First I'm going to do ordinary kriging without the covariates, then cokriging with covariates, then repeat for each site individually. 

###Kriging {.tabset .tabset-fad}

####All sites 

```{r}

coordinates(my_soil_df) <- c("lon", "lat")
coordinates(my_grid) <- c("lon", "lat")
test_dat <- my_soil_df %>% as.data.frame() %>% filter(type == "random")

#Auto Kriging

#fit variogram

Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ 1,  my_grid)
plot(Mgsqrt_vgm)


Mgsqrt_krige <- autoKrige(MgSqrt ~ 1, my_grid, my_soil_df)

```
```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")
mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod) #R squared = 0.6383

plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

The r squared was 0.6383, but the ratio between predicted and observed wasn't 1:1.

Does co-kriging improve this?

####Co-kriging all sites

```{r, warning=F}

Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ my_hue + value + chroma,  my_grid)
plot(Mgsqrt_vgm)


Mgsqrt_krige <- autoKrige(MgSqrt ~ my_hue + value + chroma, my_grid, my_soil_df)

```
```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")
mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)

plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

Cokriging actually reduced the r squared (0.5664)

I repeated the analysis with only one covariate at a time, but there wasn't much effect on the r squared compared to ordinary kriging

hue only = 0.6377    
value only = 0.5939   
chroma only = 0.6442    

####Site 1 

```{r, warning=F}
site1<- my_soil_df %>% as.data.frame() %>% filter(site == "site1")
site1_grid <- my_grid %>% as.data.frame() %>% filter(site == "site1")
test_dat <- site1 %>% as.data.frame() %>% filter(type == "random")

coordinates(site1) <- c("lon", "lat")
coordinates(site1_grid) <- c("lon", "lat")

#Ordinary kriging 


Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ 1,  site1_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ 1, site1_grid, site1)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

R squared is 0.6192, which is similar to doing all three plots at once

####Co-kriging site 1

```{r, warning=F}
Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ my_hue + value + chroma,  site1_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ my_hue + value + chroma, site1_grid, site1)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

R squared is bad = 0.1627

hue only = 0.6526   
value only =  0.1801   
chroma only = 0.6166  

####Site 2

```{r, warning=F}
site2<- my_soil_df %>% as.data.frame() %>% filter(site == "site2")
site2_grid <- my_grid %>% as.data.frame() %>% filter(site == "site2")
test_dat <- site2 %>% as.data.frame() %>% filter(type == "random")

coordinates(site2) <- c("lon", "lat")
coordinates(site2_grid) <- c("lon", "lat")

#Ordinary kriging 


Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ 1,  site2_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ 1, site2_grid, site2)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

R squared is 0.779

####Co-kriging site 2

```{r, warning=F}
Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ my_hue + value + chroma,  site2_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ my_hue + value + chroma, site2_grid, site2)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

r squared = 0.6587

hue only = 0.7771   
value only = 0.7168   
chroma only = 0.6869 

####Site 3

```{r, warning=F}
site3<- my_soil_df %>% as.data.frame() %>% filter(site == "site3")
site3_grid <- my_grid %>% as.data.frame() %>% filter(site == "site3")
test_dat <- site3 %>% as.data.frame() %>% filter(type == "random")

coordinates(site3) <- c("lon", "lat")
coordinates(site3_grid) <- c("lon", "lat")

#Ordinary kriging 


Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ 1,  site3_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ 1, site3_grid, site3)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

R squared = 0.09812, which is pretty terrible

####Co-kriging site 3


```{r, warning=F}
Mgsqrt_vgm <- autofitVariogram(MgSqrt ~ my_hue + value + chroma,  site3_grid)
plot(Mgsqrt_vgm)

Mgsqrt_krige <- autoKrige(MgSqrt ~ my_hue + value + chroma, site3_grid, site3)
```

```{r}
pred <- Mgsqrt_krige[1] %>% as.data.frame() %>%  left_join(test_dat, Mgsqrt_krige, by = c("krige_output.lon" = "lon")) %>% filter(type == "random")

mod <- lm(pred$krige_output.var1.pred ~ pred$MgSqrt)
summary(mod)
plot(pred$krige_output.var1.pred ~ pred$MgSqrt, xlab = "Observed", ylab = "Predicted")
abline(0,1)
abline(mod, col = "blue")

Mgsqrt_krige[1] %>% as.data.frame() %>% ggplot(aes(krige_output.lon, krige_output.lat, colour = krige_output.var1.pred)) +
  geom_point(size = 4) +
  my_colour
```

This fits truly badly, but then the variogram does look weird. R squared = -0.09088

hue only = -0.08056   
value only = 0.09475   
chroma only = 0.09621   