---
title: "Why different model interations predict differently"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/Users/larawootton/Documents/Honours/Data")

if(!require(pacman)){install.packages("pacman", dependencies=TRUE); library(pacman)}
p_load(ggplot2, knitr, MASS, dplyr, boral, pROC)

source("/Users/larawootton/Documents/Honours/Project_analysis/to_be_sourced.R")

soil_dat <- my_soil_df %>% 
  select(site, 
         ph_kcl,
         Na,
         C_N_ratio,
         Ca,
         Q_cover,
         elevation,
         percent_over1,
         percent_over2,
         P,
         N_perc,
         aspect,
         Clay,
         corr_dN,
         drainage,
         slope,
         type) %>% 
  filter(!is.na(type)) %>% 
  na.omit() %>% select(-type)

soil_dat[,2:16] <- scale(soil_dat[,2:16])

#Select study species (those that are present in ten or more plots) 
nb_sp <- species_df %>% select(site,
                               plot,
                               ruschia_burtoniae,
                               mesemb_1, 
                               drosanthemum_diversifolium,
                               a_delaetii,
                               a_fissum,
                               a_framesii,
                               c_spissum,
                               cephalophyllum_staminodiosum,
                               dicrocaulon,
                               oophytum) 


names(nb_sp) <- c("site", 
                  "plot",
                  "R_burtoniae", 
                  "R_comptonii", 
                  "D_diversifolium",
                  "A_delaetii",
                  "A_fissum",
                  "A_framesii",
                  "C_spissum",
                  "C_staminodiosum",
                  "Dicrocaulon_sp",
                  "Oophytum_sp")

nb_sp[is.na(nb_sp)] <- 0 #replace NA with 0

sp_occ <- nb_sp[3:12] %>% 
  apply(2, function(x) ifelse(x == 0, 0, 1)) %>% 
  as.data.frame() %>% 
  mutate(site = nb_sp$site) %>% 
  mutate(plot = nb_sp$plot) %>% 
  na.omit()

dat <- left_join(sp_occ, my_soil_df[,c(1, 5)], by = "plot") %>% 
  filter(!is.na(type),!plot == "R40 ")
type <- dat$type

all_dat <- left_join(sp_occ, my_soil_df %>% select(colnames(soil_dat[2:15]), plot), by = "plot") %>% 
  na.omit()

my_dat <- my_soil_df %>% filter(!is.na(type)) %>% na.omit() #for spatial plots
```

Previous models showed that using two sites to predict onto a third were less accurate than using randomly selected plots from across all sites.

There are four potential reasons for this.

1) Each site has a unique soil composition. Therefore predicting onto a third site is extrapolating past the information contained in the model.

2) Species may not be evenly distributed across the sites. Therefore models based on site data may not contain enough presences to create an accurate model.

3) Spatial autocorrelation may affect the ability to predict. There should be a increasing gradient in prediction accuracy as plots are chosen to minimise autocorrelation.

###Summary

1) A linear discriminant analysis showed that the sites had a unique soil composition.

2) Most species didn't occur evenly across sites.

###Site soil composition

A linear discriminant analysis based on soil variables showed that the plots clearly grouped by site. Site 1 had some overlap with sites 2 and 3, which makes sense as it was the middle plot.

```{r, echo=F}
lda_mod <- lda(site ~ ., data = soil_dat)
cols <- c("black", "red", "green")[soil_dat$site]
plot(lda_mod, col = cols)
```

###Evenness of species occurrence across sites

Species tended to be widespread in only one or two sites. Possibly could test for evenness somehow. Chi squared?

```{r, echo=F}
total <- apply(X = dat[,1:10], MARGIN = 2, FUN = sum)

site_sums <- dat %>% group_by(site) %>% summarise(R_burtoniae = sum(R_burtoniae),
                                     R_comptonii = sum(R_comptonii),
                                     D_diversifolium = sum(D_diversifolium),
                                     A_delaetii = sum(A_delaetii),
                                     A_fissum = sum(A_fissum),
                                     A_framesii = sum(A_framesii),
                                     C_spissum = sum(C_spissum),
                                     C_staminodiosum = sum(C_staminodiosum),
                                     Dicrocaulon_sp = sum(Dicrocaulon_sp),
                                     Oophytum_sp = sum(Oophytum_sp)
                                     ) 
site_sums <- rbind(site_sums[,2:11], tot = total)

sum_dat <- as.data.frame(t(site_sums[,1:10]))
colnames(sum_dat) <- c("Site 1", "Site 2", "Site 3", "Total")
kable(sum_dat, format = "html") %>% kableExtra::kable_styling(full_width = F)
```

###Spatial autocorrelation

Created seven models with decreasing amount of spatial autocorrelation. Red represents plots used in the models, blue shows plots used as test data.


```{r, echo=F, fig.width=10, fig.height=10}
par(mfrow = c(2,2))
plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site1" | my_dat$site=="site2", "red", "blue"),
     main = "Model 1: Sites 1 and 2 predicting to 3",
     ylab = "Lat",
     xlab = "")

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site3" | my_dat$site=="site1", "red", "blue"),
     main = "Model 2: Sites 1 and 3 predicting to 2",
     ylab = "",
     xlab = "")

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site3" | my_dat$site=="site2", "red", "blue"),
     main = "Model 3: Sites 2 and 3 predicting to 1",
     ylab = "Lat",
     xlab = "")

dat <- my_dat %>% group_by(site) %>% slice(1:33)
rev_dat <- setdiff(my_dat, dat)

plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 4: Use two-thirds of a site to predict onto a third",
     ylab = "",
     xlab = "",
     xlim = c(min(my_dat$lon), max(my_dat$lon)),
     ylim = c(min(my_dat$lat), max(my_dat$lat)))
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)

dat <- my_dat %>% group_by(site) %>% slice(c(1:15, 33:n()))
rev_dat <- setdiff(my_dat, dat)

plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 5: Use outer thirds of site to predict onto inner third",
     ylab = "Lat",
     xlab = "")
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$type == "grid", "red", "blue"),
     main = "Model 6: Use grid plots to predict onto random plots",
     ylab = "",
     xlab = "Lon")

set.seed(95)
rplots <- sample(150, 100)
dat <- my_dat[rplots,]
rev_dat <- my_dat[-rplots,]
plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 7: Use randomly selected plots",
     ylab = "Lat",
     xlab = "Lon")
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)
```

AUCs 

```{r, include=F, cache=T}
#mod1
load("/Users/larawootton/Documents/Honours/Data/plots12_19Aug.rda")
test <- all_dat %>% filter(site == "site3")
newpred1 <- predict.boral(plots12_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred1$linpred
pred_all1 <- ROCR::prediction(pred[,c(1:5,7:10)], test[,c(1:5,7:10)])
aucs1 <- ROCR::performance(pred_all1, "auc")
au <- unlist(aucs1@y.values)
Mod1 <- c(au[1:5], NA, au[6:9])
```

```{r, include=F, cache=T}
#mod2
load("/Users/larawootton/Documents/Honours/Data/plots13_1Aug.rda")
test <- all_dat %>% filter(site == "site2")
newpred2 <- predict.boral(plots13_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred2$linpred
pred_all2 <- ROCR::prediction(pred[,c(1, 3:7,9:10)], test[,c(1, 3:7,9:10)])
aucs2 <- ROCR::performance(pred_all2, "auc")
au <- unlist(aucs2@y.values)
Mod2 <- c(au[1], NA, au[2:6], NA, au[7:8])
```


```{r, include=F, cache=T}
#mod3
load("/Users/larawootton/Documents/Honours/Data/plots23_19Aug.rda")
test <- all_dat %>% filter(site == "site1")
newpred3 <- predict.boral(plots23_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred3$linpred
pred_all3 <- ROCR::prediction(pred, test[,1:10])
aucs3 <- ROCR::performance(pred_all3, "auc")
Mod3 <- unlist(aucs3@y.values)

```

```{r, include=F, cache=T}
#mod4
load("/Users/larawootton/Documents/Honours/Data/thirds_model.rda")
thirds_dat <- all_dat %>% group_by(site) %>% slice(1:33)
test <- setdiff(all_dat, thirds_dat)

newpred4 <- predict.boral(thirds_model, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred4$linpred
pred_all4 <- ROCR::prediction(pred, test[,1:10])
aucs4 <- ROCR::performance(pred_all4, "auc")
Mod4 <- unlist(aucs4@y.values)

```

```{r, include=F, cache=T}
#mod5
load("/Users/larawootton/Documents/Honours/Data/outer_thirds_model.rda")
outer_dat <- all_dat %>% group_by(site) %>% slice(c(1:15, 33:n()))
test <- setdiff(all_dat, outer_dat)

newpred5 <- predict.boral(outer_thirds_model, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred5$linpred
pred_all5 <- ROCR::prediction(pred[,c(1:5,7:10)], test[,c(1:5,7:10)])
aucs5 <- ROCR::performance(pred_all5, "auc")
au <- unlist(aucs5@y.values)
Mod5 <- c(au[1:5], NA, au[6:9])
```

```{r, include=F, cache=T}
#mod6
load("/Users/larawootton/Documents/Honours/Data/grid_rand_occ_27Aug.rda")
typedat <- cbind(all_dat, type = type)
grid <- typedat %>% filter(type == "grid") %>% select(-type)
test <- typedat %>% filter(type == "random") %>% select(-type)

newpred6 <- predict.boral(grid_rand_occ_27Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred6$linpred
pred_all6 <- ROCR::prediction(pred, test[,1:10])
aucs6 <- ROCR::performance(pred_all6, "auc")
Mod6 <- unlist(aucs6@y.values)

```

```{r, include=F, cache=T}
#mod7
load( "/Users/larawootton/Documents/Honours/Data/rand_mod_27Aug.rda")
set.seed(95)
rplots <- sample(150, 100)

train <- all_dat[c(rplots),]
test <- setdiff(all_dat, train)
newpred7 <- predict.boral(rand_mod_27Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred7$linpred
pred_all7 <- ROCR::prediction(pred, test[,1:10])
aucs7 <- ROCR::performance(pred_all7, "auc")
Mod7 <- unlist(aucs7@y.values)

```

```{r, echo=F}

table <- data.frame(Species = colnames(all_dat[,1:10]), 
                       Mod1, 
                       Mod2, 
                       Mod3, 
                       Mod4, 
                       Mod5,
                       Mod6,
                       Mod7) 
table[,2:8] <- round(table[,2:8], 2)
kable(table) %>% kableExtra::kable_styling(full_width = F)

```
