---
title: "The influence of spatial coverage and sample size on predicability"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/Users/larawootton/Documents/Honours/Data")

if(!require(pacman)){install.packages("pacman", dependencies=TRUE); library(pacman)}
p_load(ggplot2, knitr, MASS, dplyr, boral, pROC)

source("/Users/larawootton/Documents/Honours/Project_analysis/to_be_sourced.R")

soil_dat <- my_soil_df %>% 
  select(site, 
         ph_kcl,
         Na,
         C_N_ratio,
         Ca,
         Q_cover,
         elevation,
         percent_over1,
         percent_over2,
         P,
         N_perc,
         aspect,
         Clay,
         corr_dN,
         drainage,
         slope,
         type) %>% 
  filter(!is.na(type)) %>% 
  na.omit() %>% select(-type)

soil_dat[,2:16] <- scale(soil_dat[,2:16])

#Select study species (those that are present in ten or more plots) 
nb_sp <- species_df %>% select(site,
                               plot,
                               ruschia_burtoniae,
                               mesemb_1, 
                               drosanthemum_diversifolium,
                               a_delaetii,
                               a_fissum,
                               a_framesii,
                               c_spissum,
                               cephalophyllum_staminodiosum,
                               dicrocaulon,
                               oophytum) 


names(nb_sp) <- c("site", 
                  "plot",
                  "R_burtoniae", 
                  "R_comptonii", 
                  "D_diversifolium",
                  "A_delaetii",
                  "A_fissum",
                  "A_framesii",
                  "C_spissum",
                  "C_staminodiosum",
                  "Dicrocaulon_sp",
                  "Oophytum_sp")

nb_sp[is.na(nb_sp)] <- 0 #replace NA with 0

sp_occ <- nb_sp[3:12] %>% 
  apply(2, function(x) ifelse(x == 0, 0, 1)) %>% 
  as.data.frame() %>% 
  mutate(site = nb_sp$site) %>% 
  mutate(plot = nb_sp$plot) %>% 
  na.omit()

dat <- left_join(sp_occ, my_soil_df[,c(1, 5)], by = "plot") %>% 
  filter(!is.na(type),!plot == "R40 ")
type <- dat$type

all_dat <- left_join(sp_occ, my_soil_df %>% select(colnames(soil_dat[2:15]), plot), by = "plot") %>% 
  na.omit()

all_dat[,13:26] <- scale(all_dat[,13:26])

my_dat <- my_soil_df %>% filter(!is.na(type)) %>% na.omit() #for spatial plots
```


###Summary

1) A linear discriminant analysis showed that the sites had a unique soil composition.

2) Most species didn't occur evenly across sites.

3) Nonetheless, models of different spatial configuration predicted similarly well.

###Site soil composition

A linear discriminant analysis based on soil variables showed that the plots clearly grouped by site. Site 1 had some overlap with sites 2 and 3, which makes sense as it was the middle plot.

```{r, echo=F}
lda_mod <- lda(site ~ ., data = soil_dat)
cols <- c("black", "red", "green")[soil_dat$site]
plot(lda_mod, col = cols)
```

###Evenness of species occurrence across sites

Species tended to be widespread in only one or two sites. Possibly could test for evenness somehow. Chi squared?

```{r, echo=F}
total <- apply(X = dat[,1:10], MARGIN = 2, FUN = sum)

site_sums <- dat %>% group_by(site) %>% summarise(R_burtoniae = sum(R_burtoniae),
                                     R_comptonii = sum(R_comptonii),
                                     D_diversifolium = sum(D_diversifolium),
                                     A_delaetii = sum(A_delaetii),
                                     A_fissum = sum(A_fissum),
                                     A_framesii = sum(A_framesii),
                                     C_spissum = sum(C_spissum),
                                     C_staminodiosum = sum(C_staminodiosum),
                                     Dicrocaulon_sp = sum(Dicrocaulon_sp),
                                     Oophytum_sp = sum(Oophytum_sp)
                                     ) 
site_sums <- rbind(site_sums[,2:11], tot = total)

sum_dat <- as.data.frame(t(site_sums[,1:10]))
colnames(sum_dat) <- c("Site 1", "Site 2", "Site 3", "Total")
kable(sum_dat, format = "html") %>% kableExtra::kable_styling(full_width = F)
```

###Spatial structure

Created seven models with different spatial configurations. Red represents plots used in the models, blue shows plots used as test data. Model 7 is an average of 20 randomisations


```{r, echo=F, fig.width=10, fig.height=10}
par(mfrow = c(2,2))
plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site1" | my_dat$site=="site2", "red", "blue"),
     main = "Model 1: Sites 1 and 2 predicting to 3",
     ylab = "Lat",
     xlab = "")

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site3" | my_dat$site=="site1", "red", "blue"),
     main = "Model 2: Sites 1 and 3 predicting to 2",
     ylab = "",
     xlab = "")

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$site == "site3" | my_dat$site=="site2", "red", "blue"),
     main = "Model 3: Sites 2 and 3 predicting to 1",
     ylab = "Lat",
     xlab = "")

dat <- my_dat %>% group_by(site) %>% slice(1:33)
rev_dat <- setdiff(my_dat, dat)

plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 4: Use two-thirds of a site to predict onto a third",
     ylab = "",
     xlab = "",
     xlim = c(min(my_dat$lon), max(my_dat$lon)),
     ylim = c(min(my_dat$lat), max(my_dat$lat)))
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)

dat <- my_dat %>% group_by(site) %>% slice(c(1:15, 33:n()))
rev_dat <- setdiff(my_dat, dat)

plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 5: Use outer thirds of site to predict onto inner third",
     ylab = "Lat",
     xlab = "")
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)

plot(my_dat$lon, my_dat$lat, 
     pch = 22, cex = 1.4, 
     col = ifelse(my_dat$type == "grid", "red", "blue"),
     main = "Model 6: Use grid plots to predict onto random plots",
     ylab = "",
     xlab = "Lon")

set.seed(95)
rplots <- sample(150, 100)
dat <- my_dat[rplots,]
rev_dat <- my_dat[-rplots,]
plot(dat$lon, dat$lat,
     pch = 22, cex = 1.4, 
     col = "red",
     main = "Model 7: Use randomly selected plots",
     ylab = "Lat",
     xlab = "Lon")
points(rev_dat$lon, rev_dat$lat, 
       col = "blue",
       pch = 22, cex = 1.4)
```


```{r, include=F, cache=T}
#mod1
load("/Users/larawootton/Documents/Honours/Data/plots12_19Aug.rda")
test <- all_dat %>% filter(site == "site3")
newpred1 <- predict.boral(plots12_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred1$linpred
pred_all1 <- ROCR::prediction(pred[,c(1:5,7:10)], test[,c(1:5,7:10)])
aucs1 <- ROCR::performance(pred_all1, "auc")
au <- unlist(aucs1@y.values)
Mod1 <- c(au[1:5], NA, au[6:9])
```

```{r, include=F, cache=T}
#mod2
load("/Users/larawootton/Documents/Honours/Data/plots13_1Aug.rda")
test <- all_dat %>% filter(site == "site2")
newpred2 <- predict.boral(plots13_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred2$linpred
pred_all2 <- ROCR::prediction(pred[,c(1, 3:7,9:10)], test[,c(1, 3:7,9:10)])
aucs2 <- ROCR::performance(pred_all2, "auc")
au <- unlist(aucs2@y.values)
Mod2 <- c(au[1], NA, au[2:6], NA, au[7:8])
```


```{r mod3, include=F, cache=T}
#mod3
load("/Users/larawootton/Documents/Honours/Data/plots23_19Aug.rda")
test <- all_dat %>% filter(site == "site1")
newpred3 <- predict.boral(plots23_19Aug, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred3$linpred
pred_all3 <- ROCR::prediction(pred, test[,1:10])
aucs3 <- ROCR::performance(pred_all3, "auc")
Mod3 <- unlist(aucs3@y.values)

```

```{r, include=F, cache=T}
#mod4
load("/Users/larawootton/Documents/Honours/Data/thirds_model_scale.rda")
thirds_dat <- all_dat %>% group_by(site) %>% slice(1:33)
test <- setdiff(all_dat, thirds_dat)

newpred4 <- predict.boral(thirds_model_scale, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred4$linpred
pred_all4 <- ROCR::prediction(pred, test[,1:10])
aucs4 <- ROCR::performance(pred_all4, "auc")
Mod4 <- unlist(aucs4@y.values)

```

```{r, include=F, cache=T}
#mod5
load("/Users/larawootton/Documents/Honours/Data/outer_thirds_model_scale.rda")
outer_dat <- all_dat %>% group_by(site) %>% slice(c(1:15, 33:n()))
test <- setdiff(all_dat, outer_dat)

newpred5 <- predict.boral(outer_thirds_model_scale, 
                         newX = test[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred5$linpred
pred_all5 <- ROCR::prediction(pred[,c(1:5,7:10)], test[,c(1:5,7:10)])
aucs5 <- ROCR::performance(pred_all5, "auc")
au <- unlist(aucs5@y.values)
Mod5 <- c(au[1:5], NA, au[6:9])
```

```{r, include=F, cache=T}
#mod6
load("/Users/larawootton/Documents/Honours/Data/grid_rand_occ_29Aug_scale.rda")
typedat <- cbind(all_dat, type = type)
grid <- typedat %>% filter(type == "grid") %>% select(-type)
test2 <- typedat %>% filter(type == "random") %>% select(-type)

newpred6 <- predict.boral(grid_rand_occ_29Aug_scale, 
                         newX = test2[,13:26], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}
pred <- newpred6$linpred
pred_all6 <- ROCR::prediction(pred, test2[,1:10])
aucs6 <- ROCR::performance(pred_all6, "auc")
Mod6 <- unlist(aucs6@y.values)

```

```{r, include=F, cache=T}
#mod7
load("/Users/larawootton/Documents/Honours/Data/auc_scale10_run1_28Aug.rda")
load("/Users/larawootton/Documents/Honours/Data/auc_scale10_run2_28Aug.rda")

R_burt <- c(unlist(auc_scale10_run1_28Aug[[1]]), unlist(auc_scale10_run2_28Aug[[1]]))
R_comp <- c(unlist(auc_scale10_run1_28Aug[[2]]), unlist(auc_scale10_run2_28Aug[[2]]))
D_div <-  c(unlist(auc_scale10_run1_28Aug[[3]]), unlist(auc_scale10_run2_28Aug[[3]]))
A_del <-  c(unlist(auc_scale10_run1_28Aug[[4]]), unlist(auc_scale10_run2_28Aug[[4]]))
A_fis <-  c(unlist(auc_scale10_run1_28Aug[[5]]), unlist(auc_scale10_run2_28Aug[[5]]))
A_fra <-  c(unlist(auc_scale10_run1_28Aug[[6]]), unlist(auc_scale10_run2_28Aug[[6]]))
C_spis <- c(unlist(auc_scale10_run1_28Aug[[7]]), unlist(auc_scale10_run2_28Aug[[7]]))
C_sta <-  c(unlist(auc_scale10_run1_28Aug[[8]]), unlist(auc_scale10_run2_28Aug[[8]]))
Dicro <-  c(unlist(auc_scale10_run1_28Aug[[9]]), unlist(auc_scale10_run2_28Aug[[9]]))
Ooph <-   c(unlist(auc_scale10_run1_28Aug[[10]]),unlist(auc_scale10_run2_28Aug[[10]]))

Mod7 <- c(mean(R_burt), mean(R_comp), 
          mean(D_div), mean(A_del), 
          mean(A_fis), mean(A_fra), 
          mean(C_spis), mean(C_sta),
          mean(Dicro), mean(Ooph)) 

```
####AUCs
All models predicted almost equally well.


```{r, echo=F}

table <- data.frame(Species = colnames(all_dat[,1:10]), 
                       Mod1, 
                       Mod2, 
                       Mod3, 
                       Mod4, 
                       Mod5,
                       Mod6,
                       Mod7) 
table[,2:8] <- round(table[,2:8], 2)
kable(table) %>% kableExtra::kable_styling(full_width = F)

```

```{r, echo=F}

boxplot(table$Mod1, table$Mod2, table$Mod3,
        table$Mod4, table$Mod5, table$Mod6, table$Mod7,
        ylab = "AUC",
        xlab = "Models",
        names = c(1:7)
        )
points(c(mean(table$Mod1, na.rm = T),mean(table$Mod2,na.rm = T),
         mean(table$Mod3),mean(table$Mod4),
         mean(table$Mod5,na.rm = T),mean(table$Mod6),
         mean(table$Mod7)),
       col = "red",
       pch = 19)
```

There didn't particularly seem to be a strong pattern with sample size.

```{r, echo=F}
occ_auc <- cbind(sum_dat, table[,2:4])
occ_auc <- occ_auc %>% mutate(onetwo = apply(occ_auc[,1:2],1, sum),
                              twothree = apply(occ_auc[,2:3],1, sum),
                              onethree = apply(occ_auc[,1:3],1, sum))


plot(occ_auc$Mod1 ~ occ_auc$onetwo, 
     pch = 19,
     col = c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", 
            "orange4", "yellow2", 
            "darkblue","turquoise4" ),
     cex = 1.4,
     xlim = c(0,40),
     ylim = c(0,1),
     ylab = "AUC",
     xlab = "No. occurrences")
points(occ_auc$Mod2 ~ occ_auc$onethree,
       pch = 19,
       col = c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", 
               "orange4", "yellow2", 
               "darkblue","turquoise4" ),
       cex = 1.4)

points(occ_auc$Mod3 ~ occ_auc$twothree,
       pch = 19,
       col = c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", 
               "orange4", "yellow2", 
               "darkblue","turquoise4" ),
       cex = 1.4)

legend("bottomright", legend = table$Species, bty = "n", 
       cex = 0.7,
       col = c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", 
               "orange4", "yellow2", 
               "darkblue","turquoise4" ),
       pch = 19)
```