---
title: "Spatial distribution of species abundance"
author: "Lara Wootton"
date: "19 April 2018"
output: html_document
---
Sites 2 and 3 are mirror images of reality.   
Only species with 20 or more individuals have been plotted.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/larawootton/Documents/Honours/Data")

if(!require(pacman)){install.packages("pacman", dependencies=TRUE); library(pacman)}
p_load(dplyr, visdat, ggplot2, RColorBrewer, cowplot)

raw <- read.csv("Species_abundance_for_analysis.csv", sep = ";")

raw <- raw %>% mutate(site = c(rep("site1", 121), rep("site2", 121), rep("site3",121)))
grid <- raw %>% mutate(y = as.vector(rep(sort(c(rep(1,11), rep(2,11), rep(3,11), rep(4,11), rep(5,11), rep(6,11), rep(7,11), rep(8,11), rep(9,11), rep(10,11), rep(11,11)), decreasing = T), 3)),
                       x = as.vector(rep(rep(seq(1, 11, 1), 11), 3)))
raw$site <- as.factor(raw$site)

site1 <- grid %>% filter(site == "site1")
site2 <- grid %>% filter(site == "site2")
site3 <- grid %>% filter(site == "site3")


#Theme
theme_set(theme_bw())
my_theme <- theme(
  #axis.title.x = element_blank(),
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  panel.grid = element_blank(),
  legend.title.align = 0.5,
  legend.title = element_text(angle = 270, hjust = 1)
)
```

###Species in all three sites

####Ruschia burtoniae
```{r Ruschia burtoniae, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$ruschia_burtoniae, na.rm = T), max(grid$ruschia_burtoniae, na.rm = T)), direction = 0, name = "ruschia_burtoniae")

leg <- ggplot(site1,
              aes(x, y,
                  colour = ruschia_burtoniae)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = ruschia_burtoniae)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = ruschia_burtoniae)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = ruschia_burtoniae)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Cephalophyllum spissum
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$c_spissum, na.rm = T), max(grid$c_spissum, na.rm = T)), direction = 0, name = "c_spissum")

leg <- ggplot(site1,
              aes(x, y,
                  colour = c_spissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = c_spissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = c_spissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = c_spissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Argyroderma delaetii
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$a_delaetii, na.rm = T), max(grid$a_delaetii, na.rm = T)), direction = 0, name = "a_delaetii")

leg <- ggplot(site1,
              aes(x, y,
                  colour = a_delaetii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = a_delaetii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = a_delaetii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = a_delaetii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```


####Oophytum

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$oophytum, na.rm = T), max(grid$oophytum, na.rm = T)), direction = 0, name = "oophytum")

leg <- ggplot(site1,
              aes(x, y,
                  colour =oophytum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = oophytum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = oophytum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = oophytum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Argyroderma fissum

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$a_fissum, na.rm = T), max(grid$a_fissum, na.rm = T)), direction = 0, name = "a_fissum")

leg <- ggplot(site1,
              aes(x, y,
                  colour = a_fissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = a_fissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = a_fissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = a_fissum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Dicrocaulon

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$dicrocaulon, na.rm = T), max(grid$dicrocaulon, na.rm = T)), direction = 0, name = "dicrocaulon")

leg <- ggplot(site1,
              aes(x, y,
                  colour = dicrocaulon)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = dicrocaulon)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = dicrocaulon)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = dicrocaulon)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Drosanthemum diversifolium
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$drosanthemum_diversifolium, na.rm = T), max(grid$drosanthemum_diversifolium, na.rm = T)), direction = 0, name = "drosanthemum_diversifolium")

leg <- ggplot(site1,
              aes(x, y,
                  colour = drosanthemum_diversifolium)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = drosanthemum_diversifolium)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = drosanthemum_diversifolium)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = drosanthemum_diversifolium)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```


####Crassula deceptor

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$crassula_deceptor, na.rm = T), max(grid$crassula_deceptor, na.rm = T)), direction = 0, name = "crassula_deceptor")

leg <- ggplot(site1,
              aes(x, y,
                  colour = crassula_deceptor)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = crassula_deceptor)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = crassula_deceptor)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = crassula_deceptor)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Tylecodon pygmaeus
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$tylecodon_pygmaeus, na.rm = T), max(grid$tylecodon_pygmaeus, na.rm = T)), direction = 0, name = "tylecodon_pygmaeus")

leg <- ggplot(site1,
              aes(x, y,
                  colour = tylecodon_pygmaeus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = tylecodon_pygmaeus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = tylecodon_pygmaeus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = tylecodon_pygmaeus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Crassula columnaris
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$Crassula.sp..mini.columnus, na.rm = T), max(grid$Crassula.sp..mini.columnus, na.rm = T)), direction = 0, name = "Crassula columnaris")

leg <- ggplot(site1,
              aes(x, y,
                  colour = Crassula.sp..mini.columnus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = Crassula.sp..mini.columnus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = Crassula.sp..mini.columnus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = Crassula.sp..mini.columnus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Crassula muscova
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$crassula_muscosa, na.rm = T), max(grid$crassula_muscosa, na.rm = T)), direction = 0, name = "crassula_muscosa")

leg <- ggplot(site1,
              aes(x, y,
                  colour = crassula_muscosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = crassula_muscosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = crassula_muscosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = crassula_muscosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Caroxylon
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$caroxylon_sp1, na.rm = T), max(grid$caroxylon_sp1, na.rm = T)), direction = 0, name = "caroxylon_sp1")

leg <- ggplot(site1,
              aes(x, y,
                  colour = caroxylon_sp1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = caroxylon_sp1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = caroxylon_sp1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = caroxylon_sp1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Galenia fruticosa
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$galenia_fruticosa, na.rm = T), max(grid$galenia_fruticosa, na.rm = T)), direction = 0, name = "galenia_fruticosa")

leg <- ggplot(site1,
              aes(x, y,
                  colour = galenia_fruticosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = galenia_fruticosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = galenia_fruticosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = galenia_fruticosa)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Conophytum calculus
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$co_calculus, na.rm = T), max(grid$co_calculus, na.rm = T)), direction = 0, name = "co_calculus")

leg <- ggplot(site1,
              aes(x, y,
                  colour = co_calculus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = co_calculus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = co_calculus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = co_calculus)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

###Species in two sites

####Ruschia comptonii
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$mesemb_1, na.rm = T), max(grid$mesemb_1, na.rm = T)), direction = 0, name = "R comptonii")

leg <- ggplot(site1,
              aes(x, y,
                  colour = mesemb_1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = mesemb_1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = mesemb_1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = mesemb_1)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Argyroderma framesii

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$a_framesii, na.rm = T), max(grid$a_framesii, na.rm = T)), direction = 0, name = "a_framesii")

leg <- ggplot(site1,
              aes(x, y,
                  colour = a_framesii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = a_framesii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = a_framesii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = a_framesii)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Argyroderma framesii X delaetii

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$framesiiXD, na.rm = T), max(grid$framesiiXD, na.rm = T)), direction = 0, name = "framesiiXD")

leg <- ggplot(site1,
              aes(x, y,
                  colour = framesiiXD)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = framesiiXD)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = framesiiXD)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = framesiiXD)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```


####Conophytum subfenestratum

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$c_subfenestratum, na.rm = T), max(grid$c_subfenestratum, na.rm = T)), direction = 0, name = "c_subfenestratum")

leg <- ggplot(site1,
              aes(x, y,
                  colour = c_subfenestratum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = c_subfenestratum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = c_subfenestratum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = c_subfenestratum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Cephalophyllum staminodiosum

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$cephalophyllum_staminodiosum, na.rm = T), max(grid$cephalophyllum_staminodiosum, na.rm = T)), direction = 0, name = "cephalophyllum_staminodiosum")

leg <- ggplot(site1,
              aes(x, y,
                  colour = cephalophyllum_staminodiosum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = cephalophyllum_staminodiosum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = cephalophyllum_staminodiosum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = cephalophyllum_staminodiosum)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```


###Species in one site

####Monilaria moniliformis
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$monilaria_moniliformis, na.rm = T), max(grid$monilaria_moniliformis, na.rm = T)), direction = 0, name = "monilaria_moniliformis")

leg <- ggplot(site1,
              aes(x, y,
                  colour = monilaria_moniliformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = monilaria_moniliformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = monilaria_moniliformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = monilaria_moniliformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Monilaria pisiformis

```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$monoleria_pisiformis, na.rm = T), max(grid$monilaria_moniliformis, na.rm = T)), direction = 0, name = "monilaria_pisiformis")

leg <- ggplot(site1,
              aes(x, y,
                  colour = monoleria_pisiformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = monoleria_pisiformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = monoleria_pisiformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = monoleria_pisiformis)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```

####Sarcocornia
```{r, echo=F, fig.height=4, fig.width=12}

my_colour <- scale_color_distiller(palette = "YlGn", limits = c(min(grid$sarcocornia, na.rm = T), max(grid$sarcocornia, na.rm = T)), direction = 0, name = "sarcocornia")

leg <- ggplot(site1,
              aes(x, y,
                  colour = sarcocornia)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1")
p1 <- ggplot(site1,
             aes(x, y,
                 colour = sarcocornia)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 1") +
  theme(legend.position = "none") 

p2 <- ggplot(site2,
             aes(x, y,
                 colour = sarcocornia)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 2") +
  theme(legend.position = "none")

p3 <- ggplot(site3,
             aes(x, y,
                 colour = sarcocornia)) +
  geom_point(cex = 10, shape = 15) +
  my_theme +
  my_colour +
  labs(x = "Site 3") +
  theme(legend.position = "none")


legend <- get_legend(leg)
plot_grid(p1,p2,p3, legend, nrow = 1, rel_widths = c(0.9,0.9,0.9,0.2)) 
```