---
title: "Choosing variables and some preliminary results"
author: "Lara Wootton"
date: "15 August 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/Users/larawootton/Documents/Honours/Data")

if(!require(pacman)){install.packages("pacman", dependencies=TRUE); library(pacman)}
p_load(dismo, gbm, foreach, doParallel, TeachingDemos, boral, corrplot, pROC, ggplot2, dplyr, knitr,kableExtra)

source("/Users/larawootton/Documents/Honours/Project_analysis/to_be_sourced.R")

#Select study species (those that are present in ten or more plots) 
nb_sp <- species_df %>% select(plot, 
                               ruschia_burtoniae,
                               mesemb_1, 
                               drosanthemum_diversifolium,
                               a_delaetii,
                               a_fissum,
                               a_framesii,
                               c_spissum,
                               cephalophyllum_staminodiosum,
                               dicrocaulon,
                               oophytum) 


names(nb_sp) <- c("plot", 
                  "R_burtoniae", 
                  "R_comptonii", 
                  "D_diversifolium",
                  "A_delaetii",
                  "A_fissum",
                  "A_framesii",
                  "C_spissum",
                  "C_staminodiosum",
                  "Dicrocaulon_sp",
                  "Oophytum_sp")

nb_sp[is.na(nb_sp)] <- 0 #replace NA with 0

sp_occ <- nb_sp[2:11] %>% 
  apply(2, function(x) ifelse(x == 0, 0, 1)) %>% 
  as.data.frame() %>% 
  mutate(plot = nb_sp$plot) #Create species occurrence df

#Remove unimportant soil variables

nb_soil <- my_soil_df %>% select(-c(munsell, hue, ph_h20, dN, dC))


#Create occurrence df

occ_df <- left_join(sp_occ, nb_soil, by = "plot") %>% #Bind soil vars to species
  filter(!is.na(type)) %>% #Remove rows that we don't have data for
  select(-type, -site) #Don't need these 

occ_site_df <- left_join(sp_occ, nb_soil, by = "plot") %>% #Bind soil vars to species
  filter(!is.na(type)) %>% #Remove rows that we don't have data for
  select(-type) #keep sites for later

occ_df <- na.omit(occ_df) #remove nas
occ_site_df <- na.omit(occ_site_df)
sites <- occ_site_df$site

rm(sp_occ, nb_sp, nb_soil, occ_site_df)

```

###Summary

* Identified 14 important covariates (None of which were phosphorus).

* Optimised JSDM by scaling covariates.

* A model using all data predicted almost perfectly onto itself. 

* Models predicting onto trained and tested on different data had mixed results. Randomly selecting half the plots as training data still predicted really well onto the remaining plots. However, using two sites to predict onto a third severely decreased predictive power.

* The proportion of variance explained by the environment vs biotic interactions seemed sensitive to the data used. A similar pattern happened with the correlation results.


### Identifying important covariates

Redid the variable choice analysis in http://rpubs.com/Chopin/412588 but with lon and lat excluded. P and perc_N showed up as having a relative influence of 5% in at least one of the BRT models. The final variables used are below.

```{r}
 fin_occ_df <- dat_occ %>% 
  select(1:10, 
         ph_et_al,
         salt,
         carbon,
         Ca,
         Q_cover,
         elevation,
         percent_over1,
         percent_over2,
         P,
         N_perc,
         aspect,
         texture,
         corr_dN,
         drainage)
```


##Fitting the JSDM 

The model fit looked good with scaled covariates.

```{r, echo = F, warning=F}
load("/Users/larawootton/Documents/Honours/Data/occ_model_scaled_nospat_17Aug.rda")
par(mfrow = c(2,2))
plot.boral(occ_model_scaled_14Aug)
abline(0,1)
```

###Predicting with JSDMs

The above model was used to predict onto the same data. The AUC values were all close to one, suggesting a very good predictive power.

```{r, echo=F}
mod_fit <- fitted.boral(occ_model_scaled_nospat_17Aug, est = "mean")
pred <- as.data.frame(mod_fit$out)


pred_all <- ROCR::prediction(pred, fin_occ_df[,1:10])
rocs <- ROCR::performance(pred_all, "tpr", "fpr")

colours <- c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", "orange4", "yellow2", "darkblue","turquoise4"  )
plot(rocs, col = as.list(colours))
abline(0,1)

aucs <- ROCR::performance(pred_all, "auc")

knitr::kable(data.frame(Species = colnames(fin_occ_df[,1:10]), AUC = unlist(aucs@y.values )), digits = 3) %>% kableExtra::kable_styling(full_width = F)
```

Let's use **sites 2 and 3** to predict site 1. Some species are predicted really well, others very badly.

```{r, cache=T, include=F}
load("/Users/larawootton/Documents/Honours/Data/plots23_17Aug.rda")

site_occ <- cbind(site = sites, fin_occ_df)
plots_23 <- site_occ %>% 
  filter(!site == "site1")
plots_1 <- site_occ %>% 
  filter(site == "site1")

newpred <- predict.boral(plots23_15Aug, 
                         newX = plots_1[,12:25], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}

pred <- newpred$linpred
pred_all <- ROCR::prediction(pred, plots_1[,2:11])
rocs <- ROCR::performance(pred_all, "tpr", "fpr")
plot(rocs, col = as.list(colours))
abline(0,1)

aucs <- ROCR::performance(pred_all, "auc")

knitr::kable(data.frame(Species = colnames(plots_1[,2:11]), AUC = unlist(aucs@y.values )), digits = 3) %>% kableExtra::kable_styling(full_width = F)

```

Now **sites 1 and 2** on 3. Predictions are much worse than they were. A_framesii is not included as it didn't occur in site 3.

```{r, cache=T, include=F}
load("/Users/larawootton/Documents/Honours/Data/plots12_15Aug.rda")

site_occ <- cbind(site = sites, fin_occ_df)
plots_12 <- site_occ %>% 
  filter(!site == "site3")
plots_3 <- site_occ %>% 
  filter(site == "site3")

newpred2 <- predict.boral(plots12_15Aug, 
                         newX = plots_3[,12:25], 
                         predict.type = "marginal",
                         est = "mean")
```

```{r, echo=F}

pred <- newpred2$linpred

pred_all <- ROCR::prediction(pred[,c(1:5, 7:10)], plots_3[,c(2:6,8:11)])
rocs <- ROCR::performance(pred_all, "tpr", "fpr")
plot(rocs, col = as.list(colours))
abline(0,1)

aucs <- ROCR::performance(pred_all, "auc")

colours <- c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "orange4", "yellow2", "darkblue","turquoise4")

knitr::kable(data.frame(Species = colnames(plots_1[,c(2:6, 8:11)]), AUC = unlist(aucs@y.values )), digits = 3) %>% kableExtra::kable_styling(full_width = F)

```

Now **sites 1 and 3** on 2. Predictions are much worse than they were. R_comptonii and C_stamin are not included as it didn't occur in site 2.

```{r, include=F, cache=T}
load("/Users/larawootton/Documents/Honours/Data/plots13_15Aug.rda")
plots_13 <- site_occ %>% 
  filter(!site == "site2")
plots_2 <- site_occ %>% 
  filter(site == "site2")

newpred3 <- predict.boral(plots13_15Aug, 
                          newX = plots_2[,12:25], 
                          predict.type = "marginal",
                          est = "mean")
```

```{r, echo=F}
pred <- newpred3$linpred

pred_all <- ROCR::prediction(pred[,c(1, 3:7, 9, 10)], plots_2[,c(2,4:8, 10,11)])
rocs <- ROCR::performance(pred_all, "tpr", "fpr")

colours <- c("burlywood", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", "orange4", "darkblue","turquoise4"  )
plot(rocs, col = as.list(colours))
abline(0,1)

aucs <- ROCR::performance(pred_all, "auc")

knitr::kable(data.frame(Species = colnames(plots_2[,c(2,4:8, 10,11)]), AUC = unlist(aucs@y.values )), digits = 3) %>% kableExtra::kable_styling(full_width = F)
```

Let's try by **randomly selecting** 75 plots and predicting onto the remaining 75. It predicts a lot better than site by site.

```{r, include=F, tidy=T, cache=T}
load("/Users/larawootton/Documents/Honours/Data/train_occ_scaled_14Aug.rda")

rplots <- c(76, 37, 32,28,116,23, 48, 16, 146,  45,  18, 132,  88, 5,  43, 126,  59, 118,  38,  31,  93, 123, 136, 100, 3, 57,  86,  80,  13, 115, 112, 1, 33, 150,  68,  72,  96, 41, 95,  15,  63, 7,  29,  17, 20,  40, 109, 142,  51,  67, 19,  79,  71, 56, 149, 139,  65, 39, 6, 114, 104, 141, 145,  92,  49  ,55 , 46, 130,  66, 144,  60,  61, 137,  47,  87)

train_occ <- fin_occ_df[rplots,]
test_occ <- fin_occ_df[-rplots,]
test_covar <- as.matrix(scale(test_occ[,11:24])) 

newpred4 <- predict.boral(train_occ_scaled_14Aug, 
                         newX = test_covar, 
                         predict.type = "marginal",
                         est = "mean")
```
```{r, echo=F}
pred <- newpred4$linpred
pred_all <- ROCR::prediction(pred, test_occ[,1:10])
rocs <- ROCR::performance(pred_all, "tpr", "fpr")
colours <- c("burlywood", "firebrick2", "chocolate1","darkolivegreen1", "darkseagreen1", "green4", "orange4", "yellow2", "darkblue","turquoise4"  )

plot(rocs, col = as.list(colours))
abline(0,1)

aucs <- ROCR::performance(pred_all, "auc")
knitr::kable(data.frame(Species = colnames(test_occ[,1:10]), AUC = unlist(aucs@y.values )), digits = 3) %>% kableExtra::kable_styling(full_width = F)
```

Overall then, there is some indication that distribution is deterministic.

###Abiotic or biotic?

Boral can partition variance into that explained by environment and latent variables. However, this seems quite sensitive to the data used. The full model is shown on the left, and the randomly chosen one on the right.

```{r, echo=F, fig.width=9}

#for the full model
var <- calc.varpart(occ_model_scaled_14Aug)
part <- data.frame(enviro = var$varpart.X, bio = var$varpart.lv)

bardat <- data.frame(Species =rep(rownames(part),2), variance = c(as.vector(part[,1]), as.vector(part[,2])), type = c(rep("enviro",10), rep("lv",10)))

full <- ggplot(bardat, aes(x=Species, y=variance, fill = type)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, 
                                   colour = "black", 
                                   size = 10,
                                   vjust = 0.98, 
                                   hjust = 1),
        axis.title.x = element_blank(),
        panel.grid = element_blank()
        ) +
  labs(y = "Proportion of variance")

#for the random model

var <- calc.varpart(train_occ_scaled_14Aug)
part <- data.frame(enviro = var$varpart.X, bio = var$varpart.lv)

bardat <- data.frame(Species =rep(rownames(part),2), variance = c(as.vector(part[,1]), as.vector(part[,2])), type = c(rep("enviro",10), rep("lv",10)))

random <- ggplot(bardat, aes(x=Species, y=variance, fill = type)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, 
                                   colour = "black", 
                                   size = 10,
                                   vjust = 0.98, 
                                   hjust = 1),
        axis.title.x = element_blank(),
        panel.grid = element_blank()) +
  labs(y = "Proportion of variance")

cowplot::plot_grid(full, random)
```

###Correlations

Using the full model. Correlation due to environment on the left, correlation due to latent variables on the right. 

```{r, echo=F, fig.width=9,fig.height=8}

envcors1 <- get.enviro.cor(occ_model_scaled_14Aug)
rescors1 <- get.residual.cor(occ_model_scaled_14Aug)
par(mfrow = c(2,2))
corrplot(envcors1$sig.cor, type = "lower")
corrplot(rescors1$sig.correlaton, type = "lower")
qgraph::qgraph(envcors1$sig.cor, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)
qgraph::qgraph(rescors1$sig.correlaton, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)

```

***
Using the random model.

```{r, echo=F, fig.width=9, fig.height=8}

envcors2 <- get.enviro.cor(train_occ_scaled_14Aug)
rescors2 <- get.residual.cor(train_occ_scaled_14Aug)
par(mfrow = c(2,2))
corrplot(envcors2$sig.cor, type = "lower")
corrplot(rescors2$sig.correlaton, type = "lower")
qgraph::qgraph(envcors2$sig.cor, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)
qgraph::qgraph(rescors2$sig.correlaton, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)

```

###Important covariates

Full model

```{r, echo=F, fig.width=11, fig.height=4}
mod <- occ_model_scaled_nospat_17Aug
par(mfrow = c(1,5))

for (i in 1:5) {
  col.seq <-
    rep("black", length(mod$hpdintervals$X.coefs[i, 1:14, "lower"]))
  col.seq[mod$hpdintervals$X.coefs[i, 1:14, "lower"] < 0 &
            mod$hpdintervals$X.coefs[i, 1:14, "upper"] > 0] <- "grey"
  
  plot(
    x = c(mod$X.coefs.mean[i, 1:14]),
    y = 1:14,
    yaxt = "n",
    ylab = "",
    xlab = rownames(mod$X.coefs.mean)[i],
    col = col.seq,
    xlim = c(
      min(mod$hpdintervals$X.coefs[, 1:14, "lower"]),
      max(mod$hpdintervals$X.coefs[, 1:14, "upper"])
    ),
    pch = "x"
  )
  
  axis(
    2,
    labels = colnames(mod$X.coefs.mean),
    at = 1:14,
    las = 2,
    cex.axis = 0.75
  )
  
  segments(
    x0 = mod$hpdintervals$X.coefs[i, 1:14, "lower"],
    y0 = 1:14,
    x1 = occ_model_scaled_14Aug$hpdintervals$X.coefs[i, 1:14, "upper"],
    y1 = 1:14,
    col = col.seq
  )
  abline(v = 0, lty = 3)
  
}

```

```{r, echo=F, fig.width=11, fig.height=4}
mod <- occ_model_scaled_nospat_17Aug
par(mfrow = c(1,5))

for (i in 6:10) {
  col.seq <-
    rep("black", length(mod$hpdintervals$X.coefs[i, 1:14, "lower"]))
  col.seq[mod$hpdintervals$X.coefs[i, 1:14, "lower"] < 0 &
            mod$hpdintervals$X.coefs[i, 1:14, "upper"] > 0] <- "grey"
  
  plot(
    x = c(mod$X.coefs.mean[i, 1:14]),
    y = 1:14,
    yaxt = "n",
    ylab = "",
    xlab = rownames(mod$X.coefs.mean)[i],
    col = col.seq,
    xlim = c(
      min(mod$hpdintervals$X.coefs[, 1:14, "lower"]),
      max(mod$hpdintervals$X.coefs[, 1:14, "upper"])
    ),
    pch = "x"
  )
  
  axis(
    2,
    labels = colnames(mod$X.coefs.mean),
    at = 1:14,
    las = 2,
    cex.axis = 0.75
  )
  
  segments(
    x0 = mod$hpdintervals$X.coefs[i, 1:14, "lower"],
    y0 = 1:14,
    x1 = occ_model_scaled_14Aug$hpdintervals$X.coefs[i, 1:14, "upper"],
    y1 = 1:14,
    col = col.seq
  )
  abline(v = 0, lty = 3)
  
}

```